--- 
title: "Chapter 2 - Part C"
subtitle: "Your subtitle"
author: "Your name"
date: "`r Sys.Date()`"
output:
  bookdown::html_document2: 
    toc: TRUE
  bookdown::pdf_document2:
    toc: TRUE
link-citations: yes
fontsize: 12pt
bibliography: Bibliography_Reproducible_Science_2.bib 
csl: AmJBot.csl
---

<!--
  EEB 603 -- Reproducible Science
  Chapter 2, PART C: the finished document.

  This is what your own Chapter2_partC.Rmd should look like once you have
  worked through every section of PART C. Use it to check your work, not to
  replace it.

  Everything above the "Tables" header is the scaffolding you built in PART B
  and copied across. Everything from "Tables" down to "References" is what
  PART C added.

  Bibliography_Reproducible_Science_2.bib and AmJBot.csl must sit in the same
  folder as this file, or the document will not knit.
-->

<!-- CODE CHUNK #1: install and load dependencies, and write packages.bib -->
```{r packages, echo = FALSE, warning = FALSE, include = FALSE}
###~~~
# Load R packages
###~~~
# Create a vector w/ the required R packages
# --> If you have a new dependency, don't forget to add it in this vector
pkg <- c("knitr", "rmarkdown", "bookdown", "formattable", "kableExtra",
         "dplyr", "magrittr", "prettydoc", "htmltools", "knitcitations",
         "bibtex", "devtools")

##~~~
# 2. Check if pkg are already installed on your computer
##~~~
print("Check if packages are installed")
new.pkg <- pkg[!(pkg %in% installed.packages())]

##~~~
# 3. Install missing packages
##~~~
if(length(new.pkg) > 0){
  print(paste("Install missing package(s):", new.pkg, sep = ' '))
  # repos= names the CRAN mirror explicitly, so the install never stops to ask
  # which mirror to use. This matters when knitting: a prompt has nowhere to
  # appear and the document fails. cloud.r-project.org is CRAN's global mirror.
  install.packages(new.pkg, dependencies = TRUE, repos = "https://cloud.r-project.org/")
}else{
  print("All packages are already installed!")
}

##~~~
# 4. Load all required packages
##~~~
print("Load packages and return status")
sapply(pkg, require, character.only = TRUE)

###~~~
# Generate BibTex citation file for all loaded R packages used to produce report
###~~~
knitr::write_bib(.packages(), file = 'packages.bib')
```

# Tables

The grading scale presented in the syllabus is available in Table \@ref(tab:tabgrades).

<!-- The chunk label "tabgrades" is what \@ref(tab:tabgrades) above points at. -->
```{r tabgrades, echo = FALSE}
###~~~
# Load package (for testing)
###~~~
library(dplyr)

###~~~
# Create a data.frame w/ grading scale
###~~~
grades <- data.frame(
  Percentage = c("100-98", "97.9-93", "92.9-90", "89.9-88", "87.9-83",
                 "82.9-80", "79.9-78", "77.9-73", "72.9-70", "69.9-68",
                 "67.9-60", "59.9-0"),
  Grade = c("A+", "A", "A-", "B+", "B", "B-", "C+", "C", "C-",
            "D+", "D", "F"))

###~~~
# Plot table and add caption
###~~~
# format = "html" stops kableExtra from adding a second "Table" prefix to the
# caption ("Table Table 1:"). Leave it in.
knitr::kable(grades, caption = "Grading scale applied in this class.",
             format = "html") %>%
  kableExtra::kable_styling(c("striped", "scale_down"))
```

# Figures

The plot of the cars data is available in Figure \@ref(fig:cars).

<!-- results = "hide" keeps the summary() output out of the document. The code
     still runs, its printed output is simply not shown. -->
```{r cars, echo = FALSE, results = "hide", fig.cap = "Plot of cars' speed in relation to distance.", out.width = '100%'}
###~~~
# Load and summarize the cars dataset
###~~~
summary(cars)

###~~~
# Plot data
###~~~
plot(cars)
```

# Citing references

Parenthetical citation: reproducibility is a widespread concern across
disciplines [@Baker_2016].

In-text citation: @Baker_2016 surveyed 1,576 researchers on the subject.

<!-- Baker_2016 is the citation identifier used in
     Bibliography_Reproducible_Science_2.bib, which is named in the
     bibliography: field of the YAML above. The csl: field decides how these
     citations and the References section below are formatted: point it at a
     different .csl file and everything reformats without this text changing. -->

# References

<div id="refs"></div>

# (APPENDIX) Appendices {-}

# Appendix 1

Citations of all R packages used to generate this report.

<!-- CODE CHUNK #3: print the citations saved in packages.bib -->
```{r generateBibliography, results = "asis", echo = FALSE, warning = FALSE, message = FALSE}
###
# Load R package
###
library("knitcitations")
###
# Process and print citations in packages.bib
###
cleanbib()
options("citation_format" = "pandoc")
read.bibtex(file = "packages.bib")
```

# Appendix 2

Version information about R, the operating system (OS) and attached or R loaded
packages. This appendix was generated using `sessionInfo()`.

<!-- CODE CHUNK #4: R package versions and operating system -->
```{r sessionInfo, eval = TRUE, echo = FALSE, warning = FALSE, message = FALSE}
# Load and provide all packages and versions
sessionInfo()
```
