--- 
title: "Your title"
subtitle: "Your subtitle"
author: "Your name"
date: "`r Sys.Date()`"
output:
  bookdown::html_document2: 
    toc: TRUE
  bookdown::pdf_document2:
    toc: TRUE
link-citations: yes
fontsize: 12pt
bibliography: Bibliography_Reproducible_Science_2.bib 
csl: AmJBot.csl
---

<!--
  EEB 603 -- Reproducible Science
  Chapter 2, PART B: the finished document.

  This is what your own .Rmd should look like once you have worked through
  every section of PART B. Use it to check your work, not to replace it.

  Bibliography_Reproducible_Science_2.bib and AmJBot.csl must sit in the same
  folder as this file, or the document will not knit.
-->

<!-- CODE CHUNK #1: install and load dependencies, and write packages.bib -->
```{r packages, echo = FALSE, warning = FALSE, include = FALSE}
###~~~
# Load R packages
###~~~
# Create a vector w/ the required R packages
# --> If you have a new dependency, don't forget to add it in this vector
pkg <- c("knitr", "rmarkdown", "bookdown", "formattable", "kableExtra",
         "dplyr", "magrittr", "prettydoc", "htmltools", "knitcitations",
         "bibtex", "devtools")

##~~~
# 2. Check if pkg are already installed on your computer
##~~~
print("Check if packages are installed")
new.pkg <- pkg[!(pkg %in% installed.packages())]

##~~~
# 3. Install missing packages
##~~~
if(length(new.pkg) > 0){
  print(paste("Install missing package(s):", new.pkg, sep = ' '))
  # repos= names the CRAN mirror explicitly, so the install never stops to ask
  # which mirror to use. This matters when knitting: a prompt has nowhere to
  # appear and the document fails. cloud.r-project.org is CRAN's global mirror.
  install.packages(new.pkg, dependencies = TRUE, repos = "https://cloud.r-project.org/")
}else{
  print("All packages are already installed!")
}

##~~~
# 4. Load all required packages
##~~~
print("Load packages and return status")
sapply(pkg, require, character.only = TRUE)

###~~~
# Generate BibTex citation file for all loaded R packages used to produce report
###~~~
knitr::write_bib(.packages(), file = 'packages.bib')
```

# Your research

This is where your own text and code chunks go. Everything above this point is
the scaffolding you built in PART B; everything below "References" is generated
for you.

# References

<div id="refs"></div>

# (APPENDIX) Appendices {-}

# Appendix 1

Citations of all R packages used to generate this report.

<!-- CODE CHUNK #3: print the citations saved in packages.bib -->
```{r generateBibliography, results = "asis", echo = FALSE, warning = FALSE, message = FALSE}
###
# Load R package
###
library("knitcitations")
###
# Process and print citations in packages.bib
###
cleanbib()
options("citation_format" = "pandoc")
read.bibtex(file = "packages.bib")
```

# Appendix 2

Version information about R, the operating system (OS) and attached or R loaded
packages. This appendix was generated using `sessionInfo()`.

<!-- CODE CHUNK #4: R package versions and operating system -->
```{r sessionInfo, eval = TRUE, echo = FALSE, warning = FALSE, message = FALSE}
# Load and provide all packages and versions
sessionInfo()
```
