---
title: "Assignments"
author: ""
date: '`r Sys.Date()`'
output:
  bookdown::html_document2:
    toc: yes
    toc_float: yes
    self_contained: yes
subtitle: Evaluation forms and rubrics
link-citations: yes
fontsize: 12pt
urlcolor: blue
editor_options:
  markdown:
    wrap: sentence
---

```{js logo-js, echo=FALSE}
$(document).ready(function() {
  $('#header').parent().prepend('<div id=\"logo\"><img src=\"Images/boisestate-primarylogo-2color-rgb.png\" alt=\"\" style=\"position:absolute; top:4; right:0; padding:10px; height:120px\"></div>');
  $('#header').css('margin-right', '120px')
});
```

```{r packages, echo=FALSE, warning=FALSE, include=FALSE}
library(knitr)
library(dplyr)
library(kableExtra)
```

# How You Will Be Assessed

Every assessment in EEB 603 has an **evaluation form** setting out the criteria I use and how the points are allocated. All of them are published here, in advance.

**Please write with the relevant form open.** These forms are not something applied to your work after the fact --- they are a description of what good work looks like in this course. If anything in them is unclear, or if you think your project does not fit the criteria as written, come and talk to me *before* the deadline rather than afterwards.

Deadlines for each assessment are on the [course schedule](Timetable.html); the rules on late work and firm deadlines are in the [syllabus](index.html#LateWork).

```{r overview, echo=FALSE}
FORMS <- "Evaluation_Forms/"
pdf_link <- function(f, label = "Download pdf") sprintf("[%s](%s%s)", label, FORMS, f)

tab <- data.frame(
  Assessment = c(
    "Bioinformatics tutorial (written)",
    "Teaching the bioinformatics tutorial",
    "Individual project --- proposal",
    "Individual project --- final report",
    "Oral presentation",
    "Participation and engagement",
    "TOTAL"),
  Points = c("150", "100", "50", "150", "100", "50", "**600**"),
  `Evaluation form` = c(
    pdf_link("Bioinformatics_Tutorial_Evaluation_Form.pdf"),
    pdf_link("Teaching_Tutorial_Evaluation_Form.pdf"),
    pdf_link("Project_Proposal_Evaluation_Form.pdf"),
    pdf_link("Individual_Report_Evaluation_Form.pdf"),
    pdf_link("Oral_Presentation_Evaluation_Form.pdf"),
    "[See the syllabus](index.html#Participation)",
    ""),
  check.names = FALSE)

knitr::kable(tab,
  caption = "All assessments in EEB 603, with their point allocations and evaluation forms.",
  format = "html", row.names = FALSE) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
  row_spec(nrow(tab), bold = TRUE)
```

# The Assessments

## Bioinformatics Tutorial --- 150 points

You design a tutorial on a chapter from [PART 2](index.html#courseCont) of the course, written in *knitr*/*rmarkdown*, built around exercises that give your peers a defined set of computational skills. This is normally a **group** assignment.

The rubric covers the introduction and theoretical background, learning outcomes, package requirements, dataset description, content quality, code quality, structure, references, and submission protocol.

**Firm deadline:** your tutorial must reach me **one week before you teach it** --- your peers need that week to install packages and prepare. See the [schedule](Timetable.html) for your chapter's dates.

<a href="Evaluation_Forms/Bioinformatics_Tutorial_Evaluation_Form.pdf" class="btn btn-primary" target="_blank" rel="noopener">Bioinformatics Tutorial rubric (pdf)</a>

## Teaching the Bioinformatics Tutorial --- 100 points

You teach your tutorial to the class over two laboratory sessions, guiding your peers through the exercises and troubleshooting as they work.

The rubric covers presentation quality, explanation of key concepts, guidance through the tutorial, the exercises you developed, engagement and facilitation during the session, and professionalism.

<a href="Evaluation_Forms/Teaching_Tutorial_Evaluation_Form.pdf" class="btn btn-primary" target="_blank" rel="noopener">Teaching rubric (pdf)</a>

## Individual Project --- Proposal --- 50 points

A short proposal, due about a third of the way through the semester, setting out what you intend to do. **I read every proposal and return written feedback**, so that you can act on it while there is still most of a semester left.

Two things are asked of this proposal beyond a conventional project plan:

- **It must itself be a reproducible document** --- an R Markdown source that knits, with at least one working code chunk and a bibliography. Your proposal then becomes the skeleton of your report rather than something written once and discarded.
- **It must say where your project sits within reproducible science, and how you will know whether your approach works.** You are not expected to solve reproducibility in general; pick a part of the process, and tell me what will be reproducible at the end that is not reproducible now, and how you will test that.

<a href="Evaluation_Forms/Project_Proposal_Evaluation_Form.pdf" class="btn btn-primary" target="_blank" rel="noopener">Proposal rubric (pdf)</a>

## Individual Project --- Final Report --- 150 points

The full reproducible workflow, tailored to your thesis project or a selected publication. The rubric accommodates both **full projects** and **pre-studies** for students who do not yet have data.

The rubric covers framing of the scientific problem, use of data sources, the data management workflow, reproducible code and computational workflow, reproducibility and transparency, citations, and writing quality. The **proposal score carries forward** onto this form, giving an individual project total of 200 points.

**Deadline:** accepted up to one week late, and no later --- see the [Late Work Policy](index.html#LateWork).

<a href="Evaluation_Forms/Individual_Report_Evaluation_Form.pdf" class="btn btn-primary" target="_blank" rel="noopener">Report rubric (pdf)</a>

## Individual Project --- Oral Presentation --- 100 points

The **third and final stage of the individual project**. An 8-minute presentation of your project during the final week, to an audience of scientists who are not specialists in your area. A central goal is to show how you applied the tools and practices of reproducible science.

Taken together, the three stages --- proposal (50), report (150) and presentation (100) --- make up the individual project, worth **300 points**, or half the marks in this course. The presentation form records the combined total across all three.

The rubric covers topic introduction, scientific content, reproducible science practices, slide design, oral delivery, and accessibility to a broad audience.

<a href="Evaluation_Forms/Oral_Presentation_Evaluation_Form.pdf" class="btn btn-primary" target="_blank" rel="noopener">Presentation rubric (pdf)</a>

## Participation and Engagement --- 50 points

Attendance and engagement in [PARTS 1 and 2](index.html#courseCont). This component has no separate form; the criteria, including what counts as being present, are set out in full in the [syllabus](index.html#Participation).

# A Note on These Forms

These rubrics are themselves written in R Markdown and rendered to pdf from source held in the [course GitHub repository](https://github.com/svenbuerki/EEB603_Reproducible_Science), alongside everything else in this course. If you spot an error in one, please tell me --- and note that you now know how to fix it yourself.
