---
title: "EEB 603 -- Reproducible Science"
subtitle: "Resources"
author: "Sven Buerki - Boise State University"
date: "`r Sys.Date()`"
output:
#  bookdown::pdf_document2:
#    toc: TRUE
  bookdown::html_document2: 
    toc: TRUE
    toc_float: TRUE
    self_contained: TRUE
link-citations: yes
fontsize: 12pt
urlcolor: blue
csl: AmJBot.csl
bibliography: Bibliography_Reproducible_Science_2.bib
editor_options: 
  markdown: 
    wrap: sentence
---

```{js logo-js, echo=FALSE}
$(document).ready(function() {
  $('#header').parent().prepend('<div id=\"logo\"><img src=\"Images/boisestate-primarylogo-2color-rgb.png\" style=\"position:absolute; top:0; right:0; padding:10px; height:120px\"></div>');
  $('#header').css('margin-right', '120px')
});
```

```{r packages, echo=FALSE, warning=FALSE, include=FALSE}
library(knitr)
library(rmarkdown)
library(bookdown)
#library(distill)
library(knitcitations)
library(formatR)
library(devtools)
library(kfigr)
library(dplyr)
library(kableExtra)
library(tufte)

#Generate BibTex citation file for all R packages used to produce report
knitr::write_bib(.packages(), file = 'packages.bib')
```

<div style="text-align: right"> [Download pdf version](Resources.pdf) </div>

# Introduction

The field of reproducible science as implemented in [RStudio](https://rstudio.com/) is moving very fast and it is hard to keep up with new R packages and tools. The instructor is attempting at providing students with relevant online resources to complement class materials.   

# Podcast

The challenge of reproducing results from ten-year-old code:

  - https://www.nature.com/articles/d41586-020-02484-1

# Library of open-access books

Please find [here](https://bookdown.org) a suite of open-access books written with the R [*bookdown* package](https://github.com/rstudio/bookdown), which are relevant to the EEB603 - Reproducible Science course.

# R Markdown

Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>. Please find below additional key resources on this topic:

- **R Markdown: The Definitive Guide:** https://bookdown.org/yihui/rmarkdown/

# Writing books and complex/large documents

R Markdown can be used to produce basic HTML, PDF, and Word documents; however, more complex and larger projects can become difficult to manage in a single R Markdown file. The *bookdown* package addresses this limitation, and offers several key improvements:

- Books and reports can be built from multiple R Markdown files.
- Additional formatting features are added, such as cross-referencing, and numbering of figures, equations, and tables.
- Documents can easily be exported in a range of formats suitable for publishing, including PDF, e-books and HTML websites.

A book dedicated to this topic can be accessed [here](https://bookdown.org/yihui/bookdown/) and the package can be downloaded [here](https://CRAN.R-project.org/package=bookdown).

# Notebook

An R Notebook is an R Markdown document with chunks that can be executed independently and interactively, with output visible immediately beneath the input.

You can create a new notebook in RStudio with the menu command `File -> New File -> R Notebook`, or by using the `html_notebook` output type in your document’s YAML metadata.

# Homework assignments on RPubs

A huge number of homework assignments have been published to the website https://RPubs.com (a free publishing platform provided by RStudio), which shows that R Markdown is easy and convenient enough for students to do their homework assignments. As a TA or GA, you might even consider asking your students to complete their homework using R Markdown and publishing them on RPubs!

# Journals

Submitting scientific manuscripts written in R Markdown is still challenging; however the R [*rticles* package](https://cran.r-project.org/web/packages/rticles/index.html) was designed to simplify the creation of documents that conform to submission standards for academic journals. The package provides a suite of custom R Markdown LaTeX formats and templates for the following journals/publishers that are relevant to the EEB program:

- Biometrics articles
- Elsevier journal submissions
- Frontiers articles
- MDPI journal submissions
- PeerJ articles
- PNAS articles
- Royal Society Open Science journal submissions
- Sage journal submissions
- Springer journal submissions
- The R Journal articles
- Taylor & Francis articles

# Interactive tutorials

The R [*learnr* package](https://cran.r-project.org/web/packages/learnr/index.html) allows to turn R Markdown documents into interactive tutorials. Tutorials consist of content along with interactive components for checking and reinforcing understanding. Tutorials can include any or all of the following:

- Narrative, figures, illustrations, and equations.
- Code exercises (R code chunks that users can edit and execute directly).
- Quiz questions.
- Videos (currently supported services include YouTube and Vimeo).
- Interactive Shiny components.

Please see the full documentation (with examples) at this url: https://rstudio.github.io/learnr/

<div id="refs"></div>

# Appendix 1 {.appendix}

Citations of all R packages used to generate this report. 

```{r generateBibliography, eval = T, results="asis", cache = F, echo=F, warning = FALSE, message=FALSE}
library("knitcitations")
cleanbib()
options("citation_format" = "pandoc")
read.bibtex(file = "packages.bib")
``` 
