---
title: "Schedule"
author: ""
date: '`r Sys.Date()`'
output:
  bookdown::html_document2:
    toc: no
    toc_float: no
    self_contained: yes
subtitle:
link-citations: yes
fontsize: 12pt
urlcolor: blue
csl: AmJBot.csl
bibliography: Bibliography_Reproducible_Science_2.bib
editor_options:
  markdown:
    wrap: sentence
---

```{js logo-js, echo=FALSE}
$(document).ready(function() {
  $('#header').parent().prepend('<div id=\"logo\"><img src=\"Images/boisestate-primarylogo-2color-rgb.png\" style=\"position:absolute; top:4; right:0; padding:10px; height:120px\"></div>');
  $('#header').css('margin-right', '120px')
});
```

```{r packages, echo=FALSE, warning=FALSE, include=FALSE}
library(knitr)
library(rmarkdown)
library(bookdown)
#library(distill)
library(knitcitations)
library(formatR)
library(devtools)
library(kfigr)
library(dplyr)
library(kableExtra)
library(tufte)

#Generate BibTex citation file for all R packages used to produce report
knitr::write_bib(.packages(), file = 'packages.bib')
```

# Course Information Hub

Welcome to the central hub for course organization in EEB 603 – Reproducible Science. This webpage consolidates all essential information related to **assignment deadlines** (they are not posted in Canvas), and the **weekly schedule**.

Here you will find:

- [Assignment Deadlines](#deadlinesheader): Dates and point allocations for graded work, along with submission instructions.
- [Tentative Weekly Schedule](#schedule): Topics, and homework for each class session.

This page serves as a single reference point to help you plan your semester, stay on top of coursework, and engage fully with both theoretical and applied aspects of reproducible science.

```{r setup-dates, echo=FALSE}
###~~~
# Key dates for the semester, taken from the Boise State academic calendar:
# https://www.boisestate.edu/registrar/boise-state-academic-calendars/fall-2026-academic-calendar/
#
# Fall 2026:
#   First day of classes ............ Mon 24 Aug 2026
#   Labor Day (no classes) .......... Mon  7 Sep 2026  (falls on a Monday, so does
#                                                       not affect our Tue/Thu class)
#   Fall Break & Thanksgiving ....... Mon 23 - Sun 29 Nov 2026
#   Last day of classes ............. Fri 11 Dec 2026
#   Finals week ..................... Mon 14 - Fri 18 Dec 2026
#
# The end date below runs into finals week because the two oral-presentation
# sessions are held then. NOTE: during finals week the class meets at its
# assigned final examination slot, which may not be our usual Tue/Thu 9:00 AM.
# Confirm the slot with the Registrar and adjust if needed.
###~~~
semester_start <- as.Date("2026/08/24")   # first day of classes
semester_end   <- as.Date("2026/12/18")   # end of finals week (presentations)
break_start    <- as.Date("2026/11/23")   # Fall Break & Thanksgiving
break_end      <- as.Date("2026/11/29")
class_days     <- c("Tuesday", "Thursday")
n_weeks        <- 17

###~~~
# Build a data frame with all dates from beginning to end of Fall semester
###~~~
dates <- data.frame(seq.Date(from=semester_start, to=semester_end, by="day"))
#Assign a name to the col (allows using $)
colnames(dates) <- "Date"

###~~~
# Find weekdays associated to dates
###~~~
#Add a col to dataframe with weekday
dates$Weekday <- weekdays(dates$Date)

###~~~
# Classes only take place on Tuesday and Thursday. So, extract dates matching class weekdays
###~~~
#Subset dates based on selected weedays
datesclass <- subset(dates, dates$Weekday %in% class_days)

###~~~
# Add week ID to object from step 4
###~~~
#Create weekID vector and add it in front of dataframe
stopifnot(nrow(datesclass) == n_weeks * length(class_days))
datesclass <- data.frame(WeekID = sort(rep(seq(from=1, to=n_weeks, by=1), length(class_days))), datesclass)

###~~~
# Exclude dates falling during holiday break
###~~~
#Establish vector of dates related to holidays
holiday <- seq.Date(from=break_start, to=break_end, by="day")

#Find and exclude holidays
datesclass <- datesclass[-which(datesclass$Date %in% holiday),]

###~~~
#Read in csv with topics and tasks
###~~~
topic <- read.csv("Data/Timetable_EEB603_topic_tasks.csv")

# The csv must have exactly one row per class session. If the academic calendar
# changes the number of sessions from one year to the next, this is where it
# will bite -- data.frame() would otherwise silently recycle rows and misalign
# every topic and deadline in the table.
if (nrow(topic) != nrow(datesclass)) {
  stop(sprintf(
    "Timetable mismatch: %d class sessions but %d rows in Timetable_EEB603_topic_tasks.csv.\nAdd or remove rows in the csv so the two match.",
    nrow(datesclass), nrow(topic)))
}

###~~~
# Helper: look up the class date carrying a given deadline. Dates are derived
# from the csv rather than typed out, so the summary tables below can never
# drift away from the schedule itself.
###~~~
dl_date <- function(pattern) {
  i <- grep(pattern, topic$Deadline)
  if (!length(i)) return("TBC")
  format(datesclass$Date[i[1]], "%Y-%m-%d")
}
```

# Assignment Deadlines {#deadlinesheader}

To facilitate communication and help you plan your work, **deadlines** and **point allocations** for all assessments are provided in Table \@ref(tab:deadlines).

The bioinformatics tutorials are taught on a rolling basis, so their deadlines depend on the chapter you sign up to teach. These deadlines are listed separately in Table \@ref(tab:tutdeadlines). During the first two weeks of the semester, sign up for a chapter using the [Google Sheet](https://docs.google.com/spreadsheets/d/1gUwbqJ4gbhhSY1DfsZ7HsoDLzOKB-57xAAC1_IJ3qmk/edit?usp=sharing). Once you have signed up, find your chapter in Table \@ref(tab:tutdeadlines) and note the **two deadlines** that apply to you.

Please also read the [Late Work Policy](https://svenbuerki.github.io/EEB603_Reproducible_Science/index.html#late-work-policy) in the syllabus. In particular, **your bioinformatics tutorial must be submitted one week before you teach it. This is a firm deadline, and extensions are not available.** The individual report may be submitted up to **one week late**, but late submissions are subject to the consequences described in the [Late Work Policy](https://svenbuerki.github.io/EEB603_Reproducible_Science/index.html#late-work-policy). **I strongly recommend submitting your report by the deadline whenever possible.**

```{r deadlines, echo=FALSE}
###~~~
# Table 1: deadlines and points for all assessments
###~~~
FORMS <- "Evaluation_Forms/"
rubric <- function(file, label = "Rubric") sprintf("[%s](%s%s)", label, FORMS, file)

deadlines <- data.frame(
  Assessment = c(
    "Individual project -- proposal",
    "Bioinformatics tutorial (written)",
    "Teaching your bioinformatics tutorial",
    "Participation and engagement (PARTS 1 & 2)",
    "Individual project -- final report",
    "Oral presentation -- slides",
    "Oral presentation",
    "TOTAL"),
  Points = c("50", "150", "100", "50", "150", "--", "100", "**600**"),
  Date = c(
    dl_date("proposal"),
    "varies by chapter -- see Table 2",
    "varies by chapter -- see schedule below",
    "throughout PARTS 1 and 2",
    dl_date("Turn in individual projects"),
    dl_date("Upload slides"),
    paste(format(tail(datesclass$Date, 2), "%Y-%m-%d"), collapse = " & "),
    ""),
  Time = c("5 PM MT", "5 PM MT", "in class", "--", "5 PM MT", "5 PM MT", "in class", ""),
  `Evaluation form` = c(
    rubric("Project_Proposal_Evaluation_Form.pdf"),
    rubric("Bioinformatics_Tutorial_Evaluation_Form.pdf"),
    rubric("Teaching_Tutorial_Evaluation_Form.pdf"),
    "[Syllabus](https://svenbuerki.github.io/EEB603_Reproducible_Science/index.html#Participation)",
    rubric("Individual_Report_Evaluation_Form.pdf"),
    "--",
    rubric("Oral_Presentation_Evaluation_Form.pdf"),
    ""),
  check.names = FALSE)

knitr::kable(deadlines,
  caption = "Deadlines, point allocations and evaluation rubrics for all assessments in EEB603, Fall 2026. Times are Mountain Time. Every rubric is also on the Assignments page.",
  format = "html", row.names = FALSE) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
  row_spec(nrow(deadlines), bold = TRUE)
```

```{r tutdeadlines, echo=FALSE}
###~~~
# Table 2: bioinformatics tutorial deadlines, by chapter.
# Derived from the csv so that shifting a date in the schedule updates this too.
###~~~
i_submit <- grep("Turn in tutorial for Chap", topic$Deadline)
i_upload <- grep("Upload tutorial of Chap", topic$Deadline)
chapters <- sub(".*Chap\\. ([0-9]+).*", "\\1", topic$Deadline[i_submit])

# Dates on which each chapter's tutorial is taught in class
taught <- vapply(chapters, function(ch) {
  j <- grep(paste0("^Bioinfo\\. tutorial - Chap\\. ", ch, "$"), topic$Topic)
  if (!length(j)) return("TBC")
  paste(format(datesclass$Date[j], "%b %d"), collapse = " & ")
}, character(1))

tut <- data.frame(
  Chapter = paste("Chapter", chapters),
  `Submit to me for review` = format(datesclass$Date[i_submit], "%Y-%m-%d"),
  `Upload to Google Drive` = format(datesclass$Date[i_upload], "%Y-%m-%d"),
  `Taught in class` = as.character(taught),
  check.names = FALSE)

knitr::kable(tut,
  caption = "Bioinformatics tutorial deadlines by chapter. Find the chapter you signed up for and note your dates. Submitting to me one week before you teach is a firm deadline: your peers need that week to prepare.",
  format = "html", row.names = FALSE) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```


# Schedule {#schedule}

The full session-by-session schedule follows in Table \@ref(tab:timetab). I may adjust the schedule to accommodate the course's progress and your needs; if I do, I will let everyone enrolled know in good time and update this page, which is always the current version.

Our classes run for 75 minutes, and roughly halfway through I will call a five-minute break. I aim for a natural pause in the material rather than a fixed time on the clock, so it may fall a little either side of the midpoint.

```{r timetab, echo=FALSE}
###~~~
#Produce final timetable
###~~~

timetable <- data.frame(datesclass, topic)

# Keep only the columns students need here. The URL column is internal, and
# Deadline is deliberately dropped: deadlines now live in Tables 1 and 2 above,
# so that there is exactly one place to look them up and no risk of the two
# disagreeing after an edit.
#
# "Completed" is filled in as the semester progresses -- put a checkmark in that
# column of the csv after each session so students can see where we have got to.
timetable <- timetable[, c("WeekID", "Date", "Weekday", "Topic", "Homework", "Completed")]
colnames(timetable)[1] <- "Week"

#Some editing to better print table in pdf doc
timetable <- as.matrix(timetable)
rownames(timetable) <- rep("", nrow(timetable))
###~~~
#Plot timetable in doc
###~~~
knitr::kable(timetable,  caption = "Tentative schedule for EEB603 Reproducible Science, Fall 2026 semester.", format = "html") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

#PDF
#landscape(knitr::kable(timetable, caption = "Tentative timetable for the Reproducible Science course during the #Fall semester 2021.", booktabs = T, "latex") %>% kable_styling(latex_options = c("striped","scale_down"))
#          )


#landscape, stripped and fit width of page
#landscape(knitr::kable(timetable, caption = "Tentative timetable for EEB603 during the Fall semester 2020. #\\label{tab:tab_gg}", booktabs = T, "latex") %>% kable_styling(latex_options = c("striped","scale_down"))
#          )
```


