--- 
title: "Chapter 1"
subtitle: "Part B"
author: "Sven"
date: "`r Sys.Date()`"
output:
  bookdown::html_document2: 
    toc: TRUE
  bookdown::pdf_document2:
    toc: TRUE
link-citations: yes
fontsize: 12pt
bibliography: Bibliography_Reproducible_Science_2.bib 
csl: pnas.csl
---

<!-- GLOBAL OPTIONS -->

```{r setup, include = FALSE, cache = FALSE, message = FALSE}
# Load packages
## Add any packages specific to your code
library("knitr")
library("bookdown")
# Chunk options: see http://yihui.name/knitr/options/ ###
## Text results
opts_chunk$set(echo = TRUE, warning = TRUE, message = TRUE, include = TRUE)
## Code decoration
opts_chunk$set(tidy = TRUE, tidy.opts = list(blank = FALSE, width.cutoff = 60),
    highlight = TRUE)
## Caching code
opts_chunk$set(cache = 2, cache.path = "cache/")
## Plots
opts_chunk$set(fig.path = "Figures_MS/", dev = c("png", "pdf"),
    dpi = 300)
## Locate figures as close as possible to requested
## position (=code)
opts_chunk$set(fig.pos = "H")
```


<!-- LOAD ALL DEPENDENCIES -->
```{r packages, echo = FALSE, warning = FALSE, include = FALSE}
#Load packages
library(knitr)
library(rmarkdown)
library(bookdown)
library(formattable)
library(kableExtra)
library(dplyr)
library(magrittr)
library(prettydoc)
library(htmltools)
library(knitcitations)
library(devtools)

# Generate BibTex citation file for all R packages used to
# produce report
knitr::write_bib(.packages(), file = "packages.bib")
```

# Tables

Include a table in the RMarkdown document.

```{r tabgrades, echo = F}
# Create a data.frame w/ grading scale
grades <- data.frame(Percentage = c("100-98", "97.9-93", "92.9-90",
    "89.9-88", "87.9-83", "82.9-80", "79.9-78", "77.9-73", "72.9-70",
    "69.9-68", "67.9-60", "59.9-0"), Grade = c("A+", "A", "A-",
    "B+", "B", "B-", "C+", "C", "C-", "D+", "D", "F"))
# Plot table and add caption
knitr::kable(grades, caption = "Grading scale applied in this class.") %>%
    kable_styling(c("striped", "scale_down"))
```

# Figures

Include a figure in the RMarkdown.

```{r cars, echo=FALSE, results='hide', fig.cap="Plot of cars' speed in relation to distance.", out.width="100%"}
# Load and summarize cars dataset
summary(cars)
# Plot data
plot(cars)
```

# Cross-referencing tables and figures

## Tables

See Table \@ref(tab:tabgrades).

## Figures

See Figure \@ref(fig:cars).


# Citing publications

## Cite in parenthesis

Blah blah [see @Baker_2016, pp. 33-35; also @Smith2016, ch. 1].

## Cite in parenthesis without authors

Baker says blah blah [-@Baker_2016].

## Cite directly in the text

@Baker_2016 says blah.

# References

<div id="refs"></div>

# (APPENDIX) Appendix {-}

# Appendix 1

Citations of all R packages used to generate this report.

```{r generateBibliography, results = "asis", echo = FALSE, warning = FALSE, message = FALSE}
### Load R package
library("knitcitations")
### Process and print citations in packages.bib Clear all
### bibliography that could be in the cash
cleanbib()
# Set pandoc as the default output option for bib
options(citation_format = "pandoc")
# Read and print bib from file
read.bibtex(file = "packages.bib")
```

# Appendix 2

Version information about R, the operating system (OS) and attached or R loaded packages. This appendix was generated using `sessionInfo()`.

```{r sessionInfo, echo = FALSE, warning = FALSE, message = FALSE}
# Load and provide all packages and versions
sessionInfo()
```

