---
title: "Chapter 1 - Part A"
output: html_document
date: "2022-08-25"
---

# Headers

<!-- THIS SECTION IS ON HEADERS -->

In this section, we are working on `Markdown` syntax associated to headers (using `#`).
 
# Level 1

## Level 2

### Level 3

# Inside text commenting

Markdown does not have a syntax to add comments in your text, but this can be borrowed from HTML as follows:

```{r eval = FALSE, echo = TRUE}
# HTML syntax to comment inside text
<!-- COMMENT -->
```

You can learn more about this HTML syntax on this [webpage](https://www.w3schools.com/html/html_comments.asp).

# Lists

In this section, we learn syntax on lists.

## Unorderded lists

For sub items, use 2 tabs.

* Item 1
    - Sub item 1
        + Sub sub item 1
        + Sub sub item 2
    - Sub item 2
* Item 2

## Orderded lists

Syntax associated to ordered lists. 

1. Item 1
    - Sub Item 1
    - Sub item 2
2. Item 2
    1. Sub item 2.1
    2. Sub item 2.2
4. Item 3
5. Item 4

# Text formatting

## Italic

To italicize a word put `*` at beginning and end of word/sentence.

Italic *Italic*.

## Bold

To bold a word put `**` at beginning and end of word/sentence.

Bold **Bold**.

# Create hyperlinks

Adding hyperlinks to your documents support reproducible science and it can be easily done with the following syntax:

```{r eval=FALSE}
#Syntax to add hyperlink
[text](link)

#Example to provide hyperlink to RStudio
[RStudio](https://www.rstudio.com)
```

# Code chunks

The RMarkdown format allows integrating code chunks directly in the document, which are going to be executed and compiled to produce the final document (`HTML`).

```{r include = FALSE, eval = FALSE}
# 2+2
2+2
```

# Inline code

The result of this equation is `r 2+2`.

