---
title: "Defect log: the project we inherited"
subtitle: "EEB 603 -- Chapter 5"
author: "Your names here"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include = FALSE}
###~~~
# Global options for every chunk in this document. See Chapter 2:
# Set Global Options for Code Chunks.
###~~~
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

library(knitr)
library(kableExtra)
library(magrittr)   # for the %>% pipe
```

# What we inherited

One or two sentences: which project, which files, and which failure class your
pair owns.

# Defects we found

Each row of `Defect_log.csv` is one defect. **Add a row, re-knit, and the table
below updates itself**: the document never holds the data, so the two can never
disagree.

```{r defects}
###~~~
# Read the log and render it. The data live in the csv; this chunk only
# displays them.
###~~~
defects <- read.csv("Defect_log.csv")

knitr::kable(defects,
             caption = "Defects found in the inherited project.",
             col.names = c("File(s)", "The defect", "Repairable?",
                           "How we would fix it",
                           "The practice that would have prevented it")) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

# How many, and how bad

Inline code, as in Chapter 2, so these numbers can never go stale either.

- Defects logged: `r nrow(defects)`
- Still repairable: `r sum(grepl("^Yes", defects$repairable))`
- Permanently lost: `r sum(!grepl("^Yes", defects$repairable))`

# What we could not fix, and what we would need

List anything permanently lost, and say what single piece of information would
have prevented it. These are the strongest candidates for a charter clause.
